---
title: "Blog 1"
description: |
  We will show some tables and graphs, and we will find some interesting finding from those tables and graphs
author:
  - name: Ruiqi Tang
    url: https://example.com/norajones
date: 08-01-2021
output:
  distill::distill_article:
    self_contained: false
---

The coffee of Honduras is famous all over the world, and they are the one of the largest countries of coffee bee output. I am the big fan of Honduras coffee bee, so this is the reason why I choose Honduras. The __Covid-19__ has large impact on the their coffee industry.

I want to show some __Covid-19__ information, and we can look wheter the __Covid-19__ is still very serious in Honduras. Then, we also will find some interest information

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidycovid19)
library(tidyverse)
library(knitr)
df <- download_merged_data(cached = TRUE, silent = TRUE)

df %>%
  filter(country == "Honduras") -> covid_hnd
saveRDS(covid_hnd, "Honduras_covid.rds")
covid_hnd %>%
  select(date:recovered) -> df1
```

```{r}
df1 %>%
  select(-date) %>%
  summary() %>%
  kable()
```

This is the data summary for the Honduras data

